%!TEX program = xelatex
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[UTF8,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.425in}
\addtolength{\evensidemargin}{-0.875in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSecheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-16pt}
}

\newcommand{\resumeSubItem}[2]{\vspace{2pt}\resumeItem{#1}{#2}\vspace{-7pt}}
\newcommand{\resumeListSubItem}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\vspace{-12pt}}
\newcommand{\resumeItemListStart}{\vspace{-7pt}\begin{itemize}[fullwidth]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://aljun.me/}{\Large Yangyang Chen}} & Email : \href{mailto:gagasalamer@outlook.com}{gagasalamer@outlook.com}\\
  \href{http://aljun.me/}{Tech Blog: http://www.aljun.me} & Mobile : (86) 183-1057-6552 \\
  & Github: \href{https://github.com/salamer}{github.com/salamer}
\end{tabular*}\vspace{-10pt}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Beijing University of Chemical Technology}{Beijing}
      {School of Science / B.S. in Applied Chemistry}{Sep. 2014 - Jul. 2018}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{http://bytedance.com/}{ByteDance (Tik Tok Parent Company)}}{Beijing}
      {Software Development Engineer}{Jun 2018 - present}
      \resumeItemListStart
        \resumeItem{}
          {Responsible for the development of the fundamental + live business of the App DCar, including feeds, live broadcasts, article and video pages, IM system, private messages push, widgets(such as banner), covering App 75 \%\+ of traffic}
        \resumeItem{}
          {Led the design and execution of DCar demotion,  realizing the availability of basic service at low balance layer's functioning, keeping the service stability when traffic booming from Spring Festival's activities}
        \resumeItem{}
          {Optimized the distribution service of feed and refactory channel, realizing user channel customization, enriching subscription and prime channels. Optimized and improve distribution efficiency significantly}
        \resumeItem{}
          {In charge of the design and execution of widget resource launch, (incl. button, banner, pop-up, etc.). Satisfied the customized needs of various situations with rules engine, and developed independent protobuf generator to realize framework limitation and backward expansibility}
        \resumeItem{}
          {Led the design and execution of private message distribution. Realized users directional recall through graph database, peak clipping through message queue, and downstream stability through rate limit. Realized millions of private messages' distribution in minutes}
      \resumeItemListEnd
    \resumeSubheading
      {\href{http://baidu.com/}{Baidu (AIG, Knowledge Graph Group)}}{Beijing}
      {Algorithms Engineering Intern}{May 2017 - Aug 2017}
      \resumeItemListStart
        \resumeItem{}
          {Based on Hadoop platform, using naive bayesian method to do the data mining for all Baidu encyclopedia data, adding 3 million unknown knowledge graph data, and the accuracy rate was above 95 \%.}
        \resumeItem{}
          {Based on internal deep learning platform LegoNet, using neural network method to process the data of the search results and optimize the sorting of existing search results.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{http://megvii.com}{Megvii (Face++)}}{Beijing}
      {Software Engineering Intern}{Jun 2016 - Oct 2016}
      \resumeItemListStart
        \resumeItem{}
          {Protobuf IDL gateway generator, based on Protobuf Generator, generate complete RESTful-RPC api gateway.}
        \resumeItem{}
          {Using D3.js to write monitoring for internal deep learning training, using React to develop internal cloud interface.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://easyeasyoversea.com}{EasyEasyOversea (https://easyeasyoversea.com)}}{}
      {Independent Developer}{Jan 2017 - Feb 2017}
      \resumeItemListStart
        \resumeItem{}
          {The Best App for studying abroad. It changes and optimize the situation of information asymmetry. In the first week, The times of searches is over 100,000 +, and was contacted by three angel investors, actively sought cooperation by six major companies in the field.}
        \resumeItem{}
          {Application technologies include ElasticSearch, Redis, Django, crawlers and their scheduling, front-end side ncludes React, D3.js, Material Design}        
      \resumeItemListEnd

      % \resumeSubheading
      %   {\href{http://zhaduixueshe.com/}{ZhaDuiXueShe (http://zhaduixueshe.com)} }{}
      %   {Independent Developer}{Jul 2015 - Sep 2015}
      %   \resumeItemListStart
      %     \resumeItem{}
      %       {An academic review information sharing platform on university. Using Uwsgi and Django as service back-end, Bootstrap and JQeury for the service front-end, and Mysql as its main database.}
      %   \resumeItemListEnd

%    \resumeSubheading
%      {\href{http://zhaduixueshe.com/}{ZhaDuiXueShe Official Website (http://zhaduixueshe.com)} }{}
%      {Independent Developer}{Jul 2015 - Sep 2015}
%      \resumeItemListStart
%        \resumeItem{}
%          {Built a review material sharing platform within university. Developed the blog system for classmates to share the review materials. The website supports Markdown format posts and back-end system including online registration system and administrator-based control system.}
%        \resumeItem{}
%          {Django-based framework to build back-end using MySql. Used Nginx handling the loading and static file. Use Uwsgi and Django as service back-end. The front-end was based on the Bootstrap and JQeury.}
%      \resumeItemListEnd

    \resumeSubheading
      {\href{http://www.ict.ac.cn/}{Institute of Computing Technology, Chinese Academy of Sciences} }{Beijing}
      {Software Engineering Intern}{Dec 2016 -- Jan 2017}
      \resumeItemListStart
        \resumeItem{}
          {In the group of Yuzhong Sun, responsible for the development of a big data platform project (non-public) in the group, during which read some big data papers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------COMPETITION EXPERIENCE-----------------
\section{Competition Experiences}
  \resumeSubHeadingListStart
    \resumeSubSecheading
      {American Mathematical Modeling Contest / 2nd prize ( Honorable Mention )}{Feb 2016}
      \resumeItemListStart
        \resumeItem{}
          {Applied KNN model to build Algeria's available water resources, medical investments efficiency model}
      \resumeItemListEnd
    \resumeSubSecheading
      {Amazon AWS Hackathon, Beijing / 3rd Prize ( team leader )}{Sep 2016}
      \resumeItemListStart
        \resumeItem{}
          {Used Golang and Javascript development via gRPC, React and Docker to implement a sensor monitoring system.}
      \resumeItemListEnd
    \resumeSubSecheading
      {BloomBerg Code Your Way to Global Data / 1st prize}{Nov 2016}
      \resumeItemListStart
        \resumeItem{}
          {Wrote a automated downloading acquisitions case(PDF) script and use Word2Vec algorithms to find target}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeListSubItem
      {Renmin third prize scholarship}{Jul 2015}
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Familiar with traffic distribution services, with rich experience.}
      {}
    \resumeSubItem{Skilled in Go, familiar with Python, C, Javascript, Ruby}
      {}
    \resumeSubItem{Skilled in data structures and algorithms, web protocol, database}
      {}
    \resumeSubItem{Familiar with distributed system principles, Raft protocol, database principles}
      {}
    \resumeSubItem{Language: Mandarin(native speaker), English (CET-6), Japanese (N2)}
      {}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
